A generalized definition of multidimensional item response theory parameters

### 2024-09-03 output/paper_draft/paper_M2PLM_parameters.Rmd
Adds abstract and keywords (WiP)

---
title: "A generalized definition of multidimensional item response theory parameters"
author: "Daniel Morillo"
date: "`r format(Sys.Date(), '%d/%m/%Y')`"
output:
  officedown::rdocx_document:
    tables:
      style: APA_Like_style
    mapstyles:
      Normal: First Paragraph
    base_format: bookdown::word_document2
    reference_docx: ../../www/Template.docx
    number_sections: no
    keep_md:         no
    fig_width:       4
    fig_height:      4
bibliography: [../../www/Multidimensional-parameters-MCLM.bib, ../../www/packages.bib]
csl:          ../../www/apa-old-doi-prefix.csl
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "A generalized definition of multidimensional item response theory parameters"
author: "Daniel Morillo"
date: "`r format(Sys.Date(), '%d/%m/%Y')`"
output:
  officedown::rdocx_document:
    tables:
      style: APA_Like_style
    mapstyles:
      Normal: First Paragraph
    base_format: bookdown::word_document2
    reference_docx: ../../www/Template.docx
    number_sections: no
    keep_md:         no
    fig_width:       4
    fig_height:      4
abstract: |
  Modern measurement theory demands that Multidimensional Item Response Theory
  provides an accurate representation of covariate spaces with correlated
  dimensions and/or non-standard variances. As it is also used in applications
  in the non-cognitive domain, they also need to model negatively-keyeed items
  in an accurate and interpretable manner. Henceforth we generalize the
  multidimensional discrimination [@reckase_discriminating_1991] and
  difficulty [@reckase_difficulty_1985] parameters to account for those two
  phenomena. We do so by applying Reckase's [-@reckase_difficulty_1985] method
  in a strictly algebraic sense to the Multidimensional 2-Parameter Logistic
  Model, represented in a latent space with an arbitrary basis, and
  then defining such basis to be a concrete geometrical representation of the
  phenomena we intend to measure. Following @ackerman_creating_1994, we also
  provide a geometrical representation based on these parameters, and provide
  applied examples to illustrate the pertinence of these generalized parameters
  to accurately represent the measurement properties of the items.
keywords: |
  Multidimensional IRT, 2-Parameter Logistic model, multidimensional parameters,
  discrimination, difficulty, location, item vector representation
bibliography: [../../www/Multidimensional-parameters-MCLM.bib, ../../www/packages.bib]
csl:          ../../www/apa-old-doi-prefix.csl
editor_options: 
  chunk_output_type: console
---
